FEM Model Analysis

### 2022-03-01 FEM_R/impute_alcbase.Rmd

write_dta(final.imputed, path = 'input_data/alcbase_imputed.dta')
```

>>>>

write_dta(final.imputed, path = 'input_data/alcbase_imputed.dta')

rm(final.imputed, imp.list, imp.complete)
```

## Annual based

miss.list <- list()
# generate a separate df for each wave
imp.list <- list()
for (x in 4:9) {
  scak <- paste0('r', x, 'scako')
  alcb <- paste0('r', x, 'alcbase_a')

final.imputed <- imp.list %>% discard(is.null) %>%
                reduce(inner_join, by = "idauniq")

write_dta(final.imputed, path = 'input_data/alcbase_imputed2.dta')

### 2022-03-01 FEM_R/model_analysis_core.Rmd

  # Save plot into in E-FEM_Paper/figures/
  #ggsave(filename = paste0(cd, '_', gender, '.png'),
  #      plot = p,
  #      path = path,
  #      width = 7,
  #      height = 5)

>>>>

  p <- p + scale_fill_grey(start = .2, end = .7)
  # Save plot into in E-FEM_Paper/figures/
  #ggsave(filename = paste0(cd, '_', gender, '.png'),
  #      plot = p,
  #      path = path,
  #      width = 7,
  #      height = 5)
